---
title: "Team"
author: "Carlos A. Gonzalez"
date: "11/11/2019"
output: html_document
---


#1-4
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(ggplot2)
library(classdata)
library(tidyverse)

read.table('diabetes.txt',header=TRUE)

diabetes_reduced <- read.table("diabetes.txt", header=TRUE, na.strings=c("","NA"))


diabetes_reduced[1]= NULL
#bp.2s, and bp.2d 

diabetes_reduced

diabetes_reduced[14:15] = NULL

diabetes_cleaned = diabetes_reduced


diabetes_cleaned

index.na=apply(is.na(diabetes_cleaned), 1, any) ## identify rows with missing value.

head(diabetes_cleaned)
nrow(diabetes_cleaned)

diabetes_cleaned

```
5. use nrow to check how many rows there are also use head() to tell you how many rows there are.

6.  The best way to fix the skewness would be to cut off some of the data.  The problem with that we will not see every single variable in the data set.
```{r}
ggplot(diabetes_cleaned, aes(glyhb)) + geom_histogram()

#7.

glyhb_star= filter(diabetes_cleaned,glyhb <= 7)
glyhb_star

ggplot(glyhb_star, aes(glyhb)) + geom_histogram()



```
8.

```{r}
summary(glyhb_star)

```

10.

```{r}
 diabetes_cleaned %>% group_by(frame,location) %>% summarise (mean.glyhb= mean(glyhb))
```
11.Our main variable of interest is glyhb_star. We want to understand its relationship with ratio, bp.1s, age, gender, hip and weight. Further explore how these variables interact and visualize your findings.

```{r}
ggplot(glyhb_star, aes(glyhb,hip)) + geom_col()

ggplot(glyhb_star, aes(glyhb,bp.1s)) + geom_col()

ggplot(glyhb_star, aes(glyhb,age)) + geom_col()

ggplot(glyhb_star, aes(glyhb,gender)) + geom_col()

ggplot(glyhb_star, aes(glyhb,weight)) + geom_col()

ggplot(glyhb_star, aes(glyhb,ratio)) + geom_col()




```
12.

```{r}
ggplot(diabetes_cleaned,aes(y=weight,x=waist)) + geom_point(size = .001) + facet_wrap(~frame) +geom_jitter(colour = 'blue')
```
13. gather and spread may seem slightly unnatural to use at first, but they are very powerful functions that can transform data into the right format. Explain in your own words what the gather and spread functions do.

Gather brings columns together that have similar values.  Spread moves rows into columns that have alike values.

14.  Gather and spread are not complements because one brings columns together and then spread brings rows into columns
```{r}
fit = lm(glyhb ~stab.glu + age + waist + ratio+ factor(frame),data=diabetes_cleaned)
 summary(fit)
```

